---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit README.Rmd. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# RiksbankenAPIProject

<!-- badges: start -->
[![R-CMD-check](https://github.com/HBeijer/RiksbankenAPIProject/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/HBeijer/RiksbankenAPIProject/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

RiksbankenAPIProject retrieves interest rate and exchange rate data
from the Riksbank SWEA API.

The package provides functions to:

- List available series and their descriptions.
- Download observations for a selected series and date interval.

An internet connection is required to retrieve data.
The package requires R version 4.1.0 or newer.

## Installation

Install the package from GitHub. Setting `build_vignettes = TRUE`
includes the tutorial in the installed package.

```{r installation, eval = FALSE}
# install.packages("remotes")

remotes::install_github(
  "HBeijer/RiksbankenAPIProject",
  build_vignettes = TRUE
)
```

## Example

Load the package and find available series:

```{r available-series}
library(RiksbankenAPIProject)

series <- available_series()
head(series)
```

The returned table contains `series_id` and `description`.
Use a series identifier to download its observations.

For example, retrieve the Swedish policy rate (`SECBREPOEFF`)
during September 2026:

```{r observations}
observations <- riksbanken_serie(
  ts = "SECBREPOEFF",
  from = "2026-09-01",
  to = "2026-09-30"
)

head(observations)
```

The result is a data frame containing a `date` column of class `Date`
and a numeric `value` column.

Dates can be supplied as character strings in `YYYY-MM-DD` format
or as `Date` objects.

## Documentation

Open the help pages for the functions:

```{r function-help, eval = FALSE}
?available_series
?riksbanken_serie
```

For a tutorial with explanations and examples, open the vignette:

```{r vignette-help, eval = FALSE}
browseVignettes(package = "RiksbankenAPIProject")
```

## Authors

Thai Pham and Hampus Beijer.

## License

MIT. See [LICENSE.md](LICENSE.md) for details.
