---
title: "Using the Riksbanken API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the Riksbanken API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RiksbankenAPIProject)
```

## Introduction

RiksbankenAPIProject retrieves interest rate and exchange rate data from the Riksbank SWEA API.

This tutorial shows how to find an available series and download its observations. An internet connection is required to run these examples.

## Find available series
Use `available_series()` to retrieve a table of series identifiers and their descriptions.

```{r available-series}
series <- available_series()
head(series)
```

The table contains two columns:

- `series_id`: the identifier used when downloading observations.
- `description`: a short description of the series.

For this example, we use the Swedish policy rate, identified by `SECBREPOEFF`. We can find its description in the table:

```{r select-series}
series[series$series_id == "SECBREPOEFF", ]
```

## Download observations
Use `riksbanken_serie()` to download observations for a series and a specified date interval.

Here, we retrieve the policy rate during September 2026:

```{r download-observations}
observations <- riksbanken_serie(
  ts = "SECBREPOEFF",
  from = "2026-09-01",
  to = "2026-09-30"
)

head(observations)
```

The arguments are:

- `ts`: the series identifier.
- `from`: the start date.
- `to`: the end date.

Dates can be supplied as character strings in `YYYY-MM-DD` format or as R `Date` objects. The start date must not be later than the end date.

If dates are omitted, `from` defaults to `"1900-01-01"` and `to` defaults to the current date.

## Inspect the result

The function returns a data frame containing a `date` column of class `Date` and a numeric `value` column.

We can inspect the column types and count the observations:
```{r inspect-observations}
str(observations)
nrow(observations)
```

If the API successfully returns no observations, the function returns a data frame with zero rows and the same column types.

Invalid inputs produce an error explaining which requirement was not met. HTTP errors from the API also stop the function.
